### 2017-07-23 src/5_3_Proposal.tex
changing minor errors

VECM model parameters are traditionally obtained using ordinary least squares
(OLS) method. OLS has two main problems: is sensitive to input data errors
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} which introduces a regularization
parameter that leads to an unbiased estimation with better generalization
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available.

The proposal is to create an online algorithm based on the idea of OVECM
using either RR or its variant AAR instead of OLS 
.

@@

OVECM only considers a time varying window of historical data and uses OLS to
get solve model parameters. This proposal is about using RR or its variant AAR
as an alternative of OLS to get model parameters.

Since cointegration vectors represent a long-run relationship between the time
series, they vary little in time. This proposal also includes to obtain new
cointegration vectors only when this long-term relationship changes. This change
is detected by tracking the Mean Absolute Percentage Error (MAPE) of the last
$n$ in-sample forecasts.

@@

\begin{equation}\label{eq:vareq}
\mathbf{B} = 
\mathbf{A} \mathbf{X} + 
\mathbf{E} \, , 
\end{equation}

@@

\begin{equation}
\mathbf{B}(t) = \mathbf{A}(t) \mathbf{X}(t) + \mathbf{E}(t)\\
\label{eq:vareqt}
\end{equation}

@@

\begin{equation}
\label{eq:notation}
	\mathbf{A}(t) = 
\left[
  \begin{tabular}{c>{$}c<{$}c}
    --- & \mathbf{a}^{\top}_{t-L} & ---\\
    --- & \mathbf{a}^{\top}_{t-L+1} & ---\\
    & \vdots & \\
    --- & \mathbf{a}^{\top}_{t} & ---
  \end{tabular}
\right]
\quad \text{and} \quad
\mathbf{B}(t) =
\left[
  \begin{tabular}{c>{$}c<{$}c}
    --- & \mathbf{b}_{t-L} & ---\\
    --- & \mathbf{b}_{t-L+1} & ---\\
    & \vdots & \\
    --- & \mathbf{b}_{t} & ---
  \end{tabular}
\right] \, ,
\
\end{equation}

The RR solution $\mathbf{\hat{X}}(t)$ of equation \ref{eq:vareqt} using the
sliding window matrices defined above is:

@@

\noindent here $\lambda$ corresponds to the regularization parameter (see section
\ref{sec:regularization}). When $\lambda=0$, the solution is equivalent to OLS.

>>>>

VECM model parameters are traditionally obtained using ordinary least squares
(OLS) method. OLS has two main problems: is sensitive to input data errors
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} that introduces a regularization
parameter that leads to an unbiased estimation with better generalization
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available.

The proposal is to create an online algorithm based on the idea of OVECM
using either RR or its variant AAR instead of OLS.

@@

OVECM only considers a time varying window of historical data and uses OLS to
get model parameters. This proposal is about using RR or its variant AAR
as an alternative of OLS to estimate model parameters.

Since cointegration vectors represent a long-run relationship between the time
series, they vary little in time. This proposal also includes to obtain new
cointegration vectors only when this long-term relationship changes. This change
is detected by tracking the Mean Absolute Percentage Error (MAPE) defined in the
equation \ref{eq:MAPE}, of the last $n$ in-sample forecasts.

@@

\begin{equation*}
\mathbf{B} = 
\mathbf{A} \mathbf{X} + 
\mathbf{E} \, , 
\end{equation*}

@@

\begin{equation}
\mathbf{B}(t) = \mathbf{A}(t) \mathbf{X}(t) + \mathbf{E}(t)\\
\label{eq:vareqt1}
\end{equation}

@@

\begin{equation}
\label{eq:notation}
	\mathbf{A}(t) = 
\left[
  \begin{tabular}{c>{$}c<{$}c}
    --- & \mathbf{a}^{\top}_{t-L} & ---\\
    --- & \mathbf{a}^{\top}_{t-L+1} & ---\\
    & \vdots & \\
    --- & \mathbf{a}^{\top}_{t} & ---
  \end{tabular}
\right]
\quad \text{and} \quad
\mathbf{B}(t) =
\left[
  \begin{tabular}{c>{$}c<{$}c}
    --- & \mathbf{b}_{t-L} & ---\\
    --- & \mathbf{b}_{t-L+1} & ---\\
    & \vdots & \\
    --- & \mathbf{b}_{t} & ---
  \end{tabular}
\right] \, .
\
\end{equation}

The RR solution $\mathbf{\hat{X}}(t)$ of equation \ref{eq:vareqt1} using the
sliding window matrices defined above is:

@@

\noindent here $\lambda$ corresponds to the regularization parameter (see section
\ref{sec:regularization}). When $\lambda=0$, the solution is equivalent to the
one given by OLS.
